Dynamical dark energy constraints via clustering shells of SDSS-III BOSS galaxies

### 2017-07-13 Draft/Draft0.4.tex

\title{\sffamily Dynamical dark energy constraints via clustering shells of SDSS-III BOSS galaxies}

\author{\sffamily 
Xiao-Dong Li,$^{1,\dagger}$
Cristiano G. Sabiu,$^{2}$
Changbom Park,$^{1}$
Yuting Wang,$^{3,\star}$
Gong-bo Zhao,$^{3}$
Hyunbae Park,$^{2}$
Arman Shafieloo,$^{2}$
Juhan Kim,$^{4,1}$
and Sungwook E. Hong$^{2}$}
%Enrico Corsaro$^{1,2,3,4}$, Yueh-Ning Lee$^1$, Rafael A. Garc\'{i}a$^{1}$, Patrick Hennebelle$^1$, Savita Mathur$^{5}$, Paul G. Beck$^1$, Stephane Mathis$^1$, Dennis Stello$^{6,7}$ \& J\'er\^{o}me Bouvier$^8$}

@@

\vspace{-3.5mm}
\begin{abstract}
\sffamily
We use the anisotropic {\it clustering shells} of 1,133,326 galaxies from the Sloan Digital Sky Survey Data Release 
12 spanning the redshift range $0.15<z<0.69$ to place constraints on the expansion history of the Universe. 
Concentrating on the Chevallier-Polarski-Linder parametrization of dark energy $w=w_0+w_a\frac{z}{1+z}$,
while improving upon earlier works \citep{Li2016}, 
we present a novel use of the Alcock-Paczynski (AP) test via the small scales clustering difference between redshift bins. 
This differential measure appears to be a robust statistical tool which mitigates many systematic effects, 
allowing for competitive and unbiased constrains. 
A combination of CMB+BAO+SNIa+$H_0$+AP yields
$\Omega_m = 0.301 \pm 0.008,\ w_0 = -1.042 \pm 0.067,\ w_a = -0.07 \pm 0.29$ (68.3\% CL).
Adding the AP method reduces the $w_0-w_a$ contour area by 50\%.
The method can be combined with the standard BAO method, 
increasing the science output of ongoing and future galaxy surveys by a factor of 2.
\end{abstract}

\sffamily
{\it Introduction.}---
The  origin  of  the  accelerating  expansion  of  the  universe  is  one of  the  most  salient  questions  in  contemporary cosmology. 
Proposed mechanisms include  evolving  scalar  fields  remnant  from  the  big  bang, 
modifications to gravity,  and a  non-zero  vacuum energy \cite[see][for a comprehensive review]{2012IJMPD..2130002Y}. 
Considering the wealth of theoretical explanations, it is crucial to obtain precise and unbiased measurements of the expansion history of the Universe allowing us to 
differentiate between competing dark energy models.

@@

The Planck team has released the {\texttt {COSMOMC}} \citep{LB2002} outputs of four MCMC ``chains'' in the CPL model, 
using a combination of four datasets:
the full-mission Planck observations of CMB temperature and polarization anisotropies \cite{Planck2015},
the BAO distance priors measured from SDSS DR11 \citep{Anderson2013}, 6dFGS \citep{6dFGS} and SDSS MGS \citep{MGS},
the ``JLA'' SNIa sample \citep{JLA},
and the Hubble Space Telescope measurement of $H_0=70.6\pm3.3$ \cite{Riess2011,E14H0}.
These MCMC chains contain the CMB+BAO+SNIa+$H_0$ likelihood computed for $\sim$37,000 sets of cosmological parameters,
yielding constraints of 
\begin{equation}
 \Omega_m = 0.309 \pm 0.010, w_0 = -0.938 \pm 0.109, w_a = -0.38 \pm 0.41.
\end{equation}
%To include the AP method into the constraints,
We then compute the likelihood of the LOWZ+CMASS AP measurements for each of the parameter combinations provided in the Planck chain. 
To do this, we splited the 1,133,326 galaxies from the SDSS DR12 into six redshift bins,
measured the 2pCF in these redshift bins, 
and use a $\chi^2$ function to assess the redshift dependence.
Systematic effects are estimated via mocks made from Horizon Run 4 simulations \citep{HR4}, and subtracted when computing the $\chi^2$.
After adding the sample log-likelihoods with ours, 
while also multiply the sample weights by our likelihoods, 
we derive the CMB+BAO+SNIa+$H_0$+AP constraints on CPL parameters,
\begin{equation}
%\Omega_m = 0.300 \pm 0.008, w_0 = -1.056 \pm 0.061, w_a = -0.04 \pm 0.27,
    %1  0.2999656E+00  0.7616334E-02  0.2958745E+00  0.3035033E+00  0.2878169E+00  0.3132870E+00   \Omega_m
    %2  0.6904801E+00  0.8675444E-02  0.6808558E+00  0.6993898E+00  0.6722945E+00  0.7052207E+00   h
    %3 -0.1056468E+01  0.6096323E-01 -0.1116874E+01 -0.9965903E+00 -0.1175041E+01 -0.9287388E+00   w
    %4 -0.3808376E-01  0.2716607E+00 -0.3105235E+00  0.2321461E+00 -0.6033103E+00  0.4782076E+00   w_a    
\Omega_m = 0.301 \pm 0.008, w_0 = -1.042 \pm 0.067, w_a = -0.07 \pm 0.29.
%    1  0.3014353E+00  0.7759923E-02  0.2974325E+00  0.3048882E+00  0.2889838E+00  0.3152269E+00   \Omega_m
%    2  0.6887652E+00  0.8760036E-02  0.6797134E+00  0.6978279E+00  0.6703971E+00  0.7044224E+00   h
%    3 -0.1041626E+01  0.6732817E-01 -0.1107730E+01 -0.9768319E+00 -0.1172149E+01 -0.8979017E+00   w
%    4 -0.7173374E-01  0.2860547E+00 -0.3572176E+00  0.2107347E+00 -0.6775045E+00  0.4558817E+00   w_a    
\end{equation}
%$$.
While the central values of parameters do not shift appreciably,
the error bars of $w_0$ and $w_a$ are reduced by 38.4\% and 29.7\%, respectively.% $$-40\%$ by adding our method into the analysis.

@@

\bibitem[Ade et al. (2015)]{Planck2015}
Ade, P.A.R., Aghanim, N., \& Arnaud, M., et al. arXiv:1502.01589

\bibitem[Alam et al.(2016)]{Alam2016}
Alam, S., Ata, M., \& Bailey, S., et al. 2016,
submitted to MNRAS (arXiv:1607.03155)

%\bibitem[{{Alam} {et~al}\mbox{.}(2015{\natexlab{a}}){Alam}, {Albareti},
%  {Allende Prieto}, {Anders}, {Anderson}, {Anderton}, {Andrews}, {Armengaud},
%  {Aubourg}, {Bailey}, \& et~al.}]{dr12}
%{Alam} S., Albareti, F.D.,\& Allende Prieto, C., {et~al.}, 2015,  ApJS, 219, 12

\bibitem[Alcock \& Paczynski(1979)]{AP1979}
Alcock, C., \& Paczynski, B. 1979, Nature, 281, 358

%\bibitem[Anderson et al.(2012)]{2012MNRAS.427.3435A} 
%Anderson, L., Aubourg, E., Bailey, S., et al.\ 2012, MNRAS, 427, 3435

\bibitem[Anderson et al.(2013)]{Anderson2013}
Anderson, L., Aubourg, \'E., \& Bailey, S. et al. 2014, MNRAS, 441, 24

%\bibitem[Bassett et al.(2002)]{Bassett2002}
%Bassett, B.A., Kunz, M., Silk, J., \& Ungarelli, C. 2002, MNRAS, 336, 1217

\bibitem[Ballinger, Peacock \& Heavens 1996]{Ballinger1996}
Ballinger, W.E., Peacock, J.A., \& Heavens, A.F. 1996, MNRAS, 282, 877

\bibitem[Betoule et al.(2014)]{JLA}
Betoule, M., Kessler, R., \& Guy, J., et al. 2014, A\&A, 568, 32

\bibitem[Beutler et al.(2011)]{6dFGS}
Beutler, F., Blake, C., \& Colless, M., et al. 2011, MNRAS, 416, 3017

\bibitem[Beutler et al.(2013)]{Beutler2013}
Beutler, F., Saito, S., \& Seo, H.-J., et al. 2013, MNRAS, 443, 1065

\bibitem[Beutler et al.(2016)]{Beutler2016}
Beutler, F., Seo, H.-J., \& Saito, S., et al. 2016,
arXiv:1607.03150

\bibitem[Blake et al.(2011)]{Blake2011}
Blake, C., Glazebrook, K., \& Davis, T. M., 2011, MNRAS, 418, 1725

\bibitem[Blake et al.(2013)]{WiggleZtopoloy}
Blake, C., James, J.B., \& Poole, G.B. 2013, MNRAS, 437, 2488

\bibitem[Bolton et al.(2012)]{Bolton2012}
Bolton, A.S., Schlegel, \& D.J., Aubourg E., et al. 2012, AJ, 144, 144

\bibitem[Boylan-Kolchin et al.(2008)]{B08}
Boylan-Kolchin, M., Ma, C.-P., \& Quataert, E. 2008, MNRAS, 383, 93

%\bibitem[Bueno Belloso et al. (2012)]{BB2012}
%Bueno Belloso, A., Pettinari, G.W., Meures, N., \& Percival, W.J. 2012, Phys. Rev. D, 86, 023530

%\bibitem[Chevallier \& Polarski(2001)]{CP2001}
%Chevallier, M., Polarski, D. 2001, Int. J. Mod. Phys. D, 10, 213

%\bibitem[Choi et al.(2010)]{choi 2010}
%Choi, Y.-Y., Park, C., Kim, J., Gott, J.R., 
%Weinberg, D.H., Vogeley, M.S., \& Kim, S.S. 2010, ApJS, 190, 181

\bibitem[Christensen et al.(2001)]{Bayesian}
Christensen, N., Meyer, R., Knox, L., \& Luey, B. 2001, Class. Quant. Grav., 18, 2677

%\bibitem[Chuang et al.(2013)]{Chuang2013}
%Chuang, C.-H., Prada, F., Beutler, F., et al. 2013, arXiv:1312.4889

\bibitem[Chuang \& Wang(2012)]{ChuangWang2012}
Chuang, C.-H., \& Wang, Y. 2012, MNRAS, 426, 226

%\bibitem[Corasaniti \& Copeland(2003)]{Corasaniti2003}
%Corasaniti, P.S., Copeland, E.J. 2003, Phys. Rev. D, 67, 063521

%eBOSS: 
%http://arxiv.org/abs/1508.04473
\bibitem[Dawson et al.(2015)]{eBOSS}
Dawson, K.S., Kneib, J.P., \& Percival, W.J., et al. 2015, accepted AJ

\bibitem[Dawson et al.(2012)]{Dawson et al. 2012}
Dawson, K.S., Schlegel, D.J., \& Ahn, C.P., et al. 2012, AJ, 145, 10

\bibitem[Efstathiou (2014)]{E14H0}
Efstathiou, G. 2014, MNRAS, 440, 1138

\bibitem[Eisenstein et al.(2011)]{Eisenstein et al. 2011}
Eisenstein, D.J.,  Weinberg, D.H., \& Agolet, E., et al. 2011, AJ, 142, 72

\bibitem[Feldman, Kaiser \& Peacock (1994)]{1994ApJ...426...23F} 
Feldman, H.A., Kaiser, N., \& Peacock, J.A.\ 1994, ApJ, 426, 23

\bibitem[Fukugita et al. (1996)]{Fukugita1996}
Fukugita, M., Ichikawa, T., \& Gunn, J.E., et al. 1996, AJ, 111, 1748
%Publication:	
%Astronomical Journal v.111, p.1748

%\bibitem[Gingold \& Monaghan(1977)]{GM1977}
%Gingold, R.A., \& Monaghan, J.J. 1977, MNRAS, 181, 375

%\bibitem[Gott et al.(2009)]{gott 2009}
%Gott, J.R., Choi, Y.-Y., Park, C., \& Kim, J. 2009, ApJ, 695, L45

%\bibitem[Gott et al.(2008)]{gott 2008}
%Gott, J.R., Hambrick, D.C., Vogeley, M.S., Kim, J., Park, C., Choi, Y.-Y.,
%Cen, R., Ostriker, J.P., \& Nagamine, K. 2008, ApJ, 675, 16

\bibitem[Gunn et al. (1998)]{Gunn1998}	
Gunn, J.E., Carr, M., \& Rockosi, C. et al. 1998, AJ, 116, 3040

\bibitem[Gunn et al.(2006)]{Gunn et al. 2006}
Gunn, J.E., Siegmund, W.A., \& Mannery, E.J., et al. 2006, AJ, 131, 2332

\bibitem[Guzzo et al.(2008)]{Guzzo2008}
Guzzo, L., Pierleoni, M., \& Meneux, B., et al. 2008, Nature, 451, 541

\bibitem[Hartlap et al.(2006)]{Hartlap}
Hartlap J., Simon P. \& Schneider P. [astro-ph/0608064].

\bibitem[Hong et al.(2016)]{hong2016}
Hong, S.E., Park, C.,\&  Kim, J. 2016, ApJ, 823, 103

\bibitem[Jackson (1972)]{FOG}
Jackson, J., 1972, MNRAS, 156, 1

\bibitem[Jennings et al.(2011)]{Jennings2011}
Jennings, E., Baugh, C.M., \& Pascoli, S. 2011, MNRAS, 420, 1079

%\bibitem[Jeong et al.(2014)]{Jeong2014}
%Jeong, D., Dai, L., Kamionkowski, M., \& Szalay, A.S. 2014, arXiv:1408.4648

\bibitem[Jiang et al.(2008)]{jiang2008}
Jiang, C.Y., Jing, Y. P., \& Faltenbacher, A., et al. 2008, ApJ, 675, 1095

\bibitem[Kaiser (1987)]{Kaiser1987}
Kaiser, N. 1987, MNRAS, 227, 1

\bibitem[Kim \& Park(2006)]{kim and park 2006}
Kim, J., \& Park, C. 2006, ApJ, 639, 600

\bibitem[Kim et al.(2009)]{2009ApJ...701.1547K} 
Kim, J., Park, C., Gott, J.R., III, \& Dubinski, J.\ 2009, ApJ, 701, 1547

\bibitem[Kim et al.(2015)]{hr4}
Kim, J., Park, C., L'Huillier, B., \& Hong, S. E. 2015, JKAS, 48, 213

\bibitem[Kim et al.(2011)]{horizonrun}
Kim, J., Park, C., Rossi, G., Lee, S.M., \& Gott, J.R. 2011, JKAS, 44, 217

\bibitem[Kitaura et al.(2015)]{MDPATCHY}
Kitaura, F.S., Rodriguez-Torres, S., Chuang, C.-H., et al. arXiv:1509.06400

\bibitem[Komatsu et al.(2011)]{komatsu 2011}
Komatsu, E., Smith, K. M., \& Dunkley, J., et al. 2011, ApJS, 192, 18

\bibitem[Lacey \& Cole(1993)]{LC93}
Lacey, C., \& Cole, S. 1993, MNRAS, 262, 627

\bibitem[Landy \& Szalay(1993)]{1993ApJ...412...64L} 
Landy, S.D., \& Szalay, A.S.\ 1993, ApJ, 412, 64

%EUCLID:
%http://arxiv.org/abs/1110.3193
\bibitem[Laureijs et al.(2011)]{EUCLID}
Laureijs, R., Amiaux, J., \& Arduini, S., et al. 2011, arXiv:1110.3193

\bibitem[Lavaux \& Wandelt(2012)]{LavausWandelt1995}
Lavaux, G., \& Wandelt, B.D. 2012, ApJ, 754, 109

%\bibitem[Levi et al.(2013)]{2013arXiv1308.0847L} 
%Levi, M., Bebek, C., Beers, T., et al.\ 2013, arXiv:1308.0847

\bibitem[Lewis \& Bridle (2002)]{LB2002}
Lewis, A., \& Bridle, S. 2002, Phys. Rev. D, 66, 103511

\bibitem[L'Huillier et al.(2014)]{2014NewA...30...79L} 
L'Huillier, B., Park, C., \& Kim, J.\ 2014, New Astronomy, 30, 79

\bibitem[Li et al.(2011)]{Li2011}
Li, M., Li, X.-D., Wang, S., \& Wang, Y. 2011, Commun. Theor. Phys., 56, 525

\bibitem[Li et al.(2014)]{Li2014}
Li, X.-D., Park, C., Forero-Romero, J., \& Kim, J. 2014, ApJ, 796, 137

\bibitem[Li et al.(2015)]{Li2015}
Li, X.-D., Park, C., Sabiu, C.G., \& Kim, J. 2015, MNRAS, 450, 807

\bibitem[Li et al.(2016)]{Li2016}
Li, X.-D., Park, C., \& Sabiu, C.G., et al. 2016, ApJ, 832, 103

%\bibitem[Linder(2003)]{Linder2003}
%Linder, E.V. 2003, Phys. Rev. Lett., 90, 091301

\bibitem[Linder et al.(2014)]{Linder2013}
Linder, E.V., Minji, O., Okumura, T., Sabiu, C.G., \& Song, Y.-S. 2014, Phys. Rev. D, 89, 063525

\bibitem[L{\'o}pez-Corredoira(2014)]{2014ApJ...781...96L} 
L{\'o}pez-Corredoira, M.\ 2014, ApJ, 781, 96

\bibitem[Mao et al. (2016)]{Qingqing2016}
Mao, Q., Berlind, A.A., Scherrer, R.J., et al. 2016, submitted to ApJ

\bibitem[Marinoni \& Buzzi(2010)]{Marinoni2010}
Marinoni, C., \& Buzzi, A. 2010, Nature, 468, 539

\bibitem[Matsubara \& Suto(1996)]{Matsubara1996}
Matsubara T., \& Suto, Y. 1996, ApJ, 470, L1

\bibitem[McCavana et al.(2012)]{M12}
McCavana, T., Micic, M., Lewis, G. F., et al. 2012, MNRAS, 424, 361

\bibitem[Morandi \& Sun (2016)]{MS2016}
Morandi, A., \& Sun, M. arXiv:1601.03741

\bibitem[Outram et al.(2004)]{Outram2004}
Outram, P.J., Shanks, T., Boyle, B.J., Croom, S.M., Hoyle, F., Loaring, N.S., 
Miller, L., \& Smith, R.J. 2004, MNRAS, 348, 745

%\bibitem[Parejko et al.(2013)]{Parejko2013}
%Parejko, J. K., Sunayama, T., Padmanabhan, N., et al. 2013, MNRAS, 429, 98

\bibitem[Parejko et al.(2013)]{Parejko2013}
Parejko J.K., et al., 2013, MNRAS, 429, 98

\bibitem[Parihar et al. (2014)]{CMASSLSS2014}
Parihar, P., Vogeley, M.S., \& Gott, J.R., et al. 2014, ApJ, 796, 86

\bibitem[Park et al.(2005)]{park 2005}
Park, C., Kim, J., \& Gott, J.R. 2005, ApJ, 633, 1

\bibitem[Park \& Kim(2010)]{topology}
Park, C., \& Kim, Y.-R. 2010, ApJL, 715, L185

\bibitem[Park et al. (2012)]{Park2012}
Park, C., Choi, Y.-Y., Kim, J., Gott, J.R., Kim, S.S., \&
Kim, K.-S. 2012, ApJ, 759, 7

\bibitem[Park et al. (2015)]{Park2015}
Park, C., Song, H., Einasto, M., Lietzen, H., \&
Heinamaki, P. 2015, JKAS, 48, 75

\bibitem[Peebles \& Ratra(2003)]{PR2003}
Peebles, P.J.E., \& Ratra, B. 2003, Reviews of Modern Physics, 75, 559

\bibitem[Percival et al.(2014)]{Percival2014}
Percival, W.J., Ross, A.J., \& S\'{a}nchez, A.G., et al. 2014, MNRAS, 439, 2531

\bibitem[Perlmutter et al.(1999)]{Perl1999}
Perlmutter, S., Aldering, G., \& Goldhaber, G., et al. 1999, ApJ, 517, 565

\bibitem[Press \& Shechter(1974)]{PS1974}
Press, W.H., \& Schechter, P.L. 1974, ApJ, 187, 425

\bibitem[Reid et al.(2012)]{Reid2012}
Reid, B., Samushia, L., \& White, M., et al. 2012, MNRAS, 426, 2719

\bibitem[Reid et al.(2016)]{Reidetal:2016}
Reid, B., Ho, S., \& Padmanabhan, N., et al.  2016, MNRAS, 455, 1553

\bibitem[Riess et al.(1998)]{Riess1998}
Riess, A.G., Filippenko, A.V., \& Challis, P., et al. 1998, AJ, 116, 1009

\bibitem[Riess et al.(2011)]{Riess2011}
Riess, A.G., Macri, L., \& Casertano, S., et al. 2011, ApJ, 730, 119
%A 3\% Solution: Determination of the Hubble Constant with the Hubble Space Telescope and Wide Field Camera

\bibitem[Ross et al.(2012)]{2012MNRAS.424..564R} 
Ross, A.J., Percival, W.J., \& S{\'a}nchez, A.G. et al.\ 2012, MNRAS, 424, 564

\bibitem[Ross et al.(2015)]{MGS}
Ross, A.J., Samushia, L., \& Howlett, C., et al. 2015, MNRAS, 449, 835

\bibitem[Ryden(1995)]{Ryden1995}
Ryden, B.S. 1995, ApJ, 452, 25

%\bibitem[Samushia et al.(2014)]{Samushia2014}
%Samushia, L., Reid, B. A., White, M., et al. 2014, MNRAS, 439, 3504

%\bibitem[Sanchez et al.(2013)]{Sanchez2013}
%Sanchez, A. G., Kazin, E. A., Beutler, F., et al. 2013, MNRAS, 433, 1202

%\bibitem[Sutter et al.(2014)]{Sutter2014}
%Sutter, P.M., Pisani, A., Wandelt, B.D., \& Weinberg, D.H. 2014, MNRAS, 443, 2983

\bibitem[Sanchez et al.(2016)]{Sanchez2016}
Sanchez, A. G., Scoccimarro, R., \& Crocce, M., et al.
arXiv:1607.03147

\bibitem[Schlafly et al.(2010)]{Schlafly2010}
Schlafly E.F., Finkbeiner D.P., Schlegel D.J., et al. 2010, ApJ, 725, 1175

\bibitem[Schlafly \& Finkbeiner(2011)]{SF2011}
Schlafly E.F., \& Finkbeiner D.P. 2011, ApJ, 737, 103

%DESI:
%http://arxiv.org/abs/1106.1706
\bibitem[Schlegel et al.(2011)]{DESI}
Schlegel, D., Abdalla, F., \& Abraham, T., et al. 2011, arXiv:1106.1706

\bibitem[Smee et al.(2013)]{Smee2013}
Smee, S.A., Gunn, J.E., \& Uomoto, A., et al. 2013, AJ, 146, 32

\bibitem[Song et al.(2014)]{2014arXiv1407.2257S} 
Song, Y.S., Sabiu, C.G., 
Okumura, T., Oh, M., \& Linder, E.V.\ 2014, JCAP, 12, 005

\bibitem[Speare et al. (2015)]{Speare2015}
Speare, R., Gott, J.R., Kim, J., \& Park, C.
2015, ApJ, 799, 176

%\bibitem[Tojeiro \& Percival(2011)]{Tojeiro2011}
%Tojeiro R., \& Percivial W.J. 2011, MNRAS, 417, 1114

%\bibitem[Tojeiro et al.(2012)]{Tojeiro2012}
%Tojeiro, R., Percival, W. J., Wake, D. A., et al. 2012, MNRAS, 424, 136

\bibitem[Viana \& Liddle(1996)]{VL1996}
Viana, P.T.P., \& Liddle, A.R. 1996, MNRAS, 281, 323

\bibitem[Villalobos et al.(2013)]{V13}
Villalobos, \'{A}., ́De Lucia, G., Weinmann, S.M., Borgani, S., \& Murante, G. 2013, MNRAS, 433, L49

\bibitem[Weinberg (1989)]{SW1989}
Weinberg, S. 1989, Reviews of Modern Physics, 61, 1

\bibitem[White (2011)]{White2011}
White M., et al. 2011, ApJ, 728, 126

\bibitem[Yoo \& Watanabe(2012)]{2012IJMPD..2130002Y} Yoo, J., \& Watanabe, Y.\ 2012, International Journal of Modern Physics D, 21, 1230002

\bibitem[York et al.(2000)]{York et al. 2000}
York, D.G., Adelman, J., \& Anderson, J.E., et al. 2000, AJ, 120, 1579

\bibitem[Zehavi et al.(2011)]{zehavi2011}
Zehavi, I., Zheng, Z., \& Weinberg, D.H., et al. 2011, ApJ, 736, 59

%\bibitem{Milliman14}
%\bibinfo{author}{Milliman}, K.~E. {\it et~al.}
%\newblock \bibinfo{title}{WIYN Open Cluster Study. LX. Spectroscopic Binary Orbits in NGC 6819.}
%\newblock{\it Astron. \ J.}{\bf\, 148}, 38--57 (2014).

@@

\begin{thebibliography}{10}
\setcounter{enumiv}{29}

>>>>

\title{%\sffamily 
Dynamical dark energy constraints via clustering shells of SDSS-III BOSS galaxies}

\author{%\sffamily 
Xiao-Dong Li,$^{1}$
Cristiano G. Sabiu,$^{2}$
Changbom Park,$^{1}$
Yuting Wang,$^{3}$
Gong-bo Zhao,$^{3}$
Hyunbae Park,$^{2}$
Arman Shafieloo,$^{2}$
Juhan Kim,$^{4,1}$
and Sungwook E. Hong$^{2}$}
%Enrico Corsaro$^{1,2,3,4}$, Yueh-Ning Lee$^1$, Rafael A. Garc\'{i}a$^{1}$, Patrick Hennebelle$^1$, Savita Mathur$^{5}$, Paul G. Beck$^1$, Stephane Mathis$^1$, Dennis Stello$^{6,7}$ \& J\'er\^{o}me Bouvier$^8$}

@@

\vspace{-3.5mm}
\begin{abstract}
%\sffamily
We use the anisotropic {\itshape clustering shells} of 1,133,326 galaxies from the Sloan Digital Sky Survey Data Release 
12 spanning the redshift range  $0.15<z<0.69$ to place constraints on the expansion history of the Universe. 
Concentrating on the Chevallier-Polarski-Linder parametrization of dark energy $w=w_0+w_a\frac{z}{1+z}$,
while improving upon earlier works \citep{Li2016}, 
we present a novel use of the Alcock-Paczynski (AP) test via the small scales clustering difference between redshift bins. 
This differential measure appears to be a robust statistical tool which mitigates many systematic effects, 
allowing for competitive and unbiased constrains. 
A combination of CMB+BAO+SNIa+$H_0$+AP yields
$\Omega_m = 0.301 \pm 0.008,\ w_0 = -1.042 \pm 0.067,\ w_a = -0.07 \pm 0.29$ (68.3\% CL).
Adding the AP method reduces the $w_0-w_a$ contour area by 50\%.
The method can be combined with the standard BAO method, 
increasing the science output of ongoing and future galaxy surveys by a factor of 2.
\end{abstract}

%\sffamily
%{\it Introduction.}---
The  origin  of  the  accelerating  expansion  of  the  universe  is  one of  the  most  salient  questions  in  contemporary cosmology. 
Proposed mechanisms include  evolving  scalar  fields  remnant  from  the  big  bang, 
modifications to gravity,  and a  non-zero  vacuum energy (see \cite{2012IJMPD..2130002Y} for a comprehensive review). 
Considering the wealth of theoretical explanations, it is crucial to obtain precise and unbiased measurements of the expansion history of the Universe allowing us to 
differentiate between competing dark energy models.

@@

The Planck team has released the {\texttt {COSMOMC}} \citep{LB2002} outputs of four MCMC ``chains'' in the CPL model, 
using a combination of four datasets:
the full-mission Planck observations of CMB temperature and polarization anisotropies \cite{Planck2015},
the BAO distance priors measured from SDSS DR11 \citep{Anderson2013}, 6dFGS \citep{6dFGS} and SDSS MGS \citep{MGS},
the ``JLA'' SNIa sample \citep{JLA},
and the Hubble Space Telescope measurement of $H_0=70.6\pm3.3$ \cite{Riess2011,E14H0}.
These MCMC chains contain the CMB+BAO+SNIa+$H_0$ likelihood computed for $\sim$37,000 sets of cosmological parameters,
yielding constraints of 
\begin{equation}
 \Omega_m = 0.309 \pm 0.010, w_0 = -0.938 \pm 0.109, w_a = -0.38 \pm 0.41.
\end{equation}
%To include the AP method into the constraints,
We then compute the likelihood of the LOWZ+CMASS AP measurements for each of the parameter combinations provided in the Planck chain. 
To do this, we splited the 1,133,326 galaxies from the SDSS DR12 into six redshift bins,
measured the 2pCF in these redshift bins, 
subtract the systematic effects based on estimations from mocks made from Horizon Run 4 simulations \citep{HR4},
and use a $\chi^2$ function to assess the redshift dependence
(see Methods for further explanations).
After adding the sample log-likelihoods with ours, 
while also multiply the sample weights by our likelihoods, 
we derive the CMB+BAO+SNIa+$H_0$+AP constraints on CPL parameters,
\begin{equation}
%\Omega_m = 0.300 \pm 0.008, w_0 = -1.056 \pm 0.061, w_a = -0.04 \pm 0.27,
    %1  0.2999656E+00  0.7616334E-02  0.2958745E+00  0.3035033E+00  0.2878169E+00  0.3132870E+00   \Omega_m
    %2  0.6904801E+00  0.8675444E-02  0.6808558E+00  0.6993898E+00  0.6722945E+00  0.7052207E+00   h
    %3 -0.1056468E+01  0.6096323E-01 -0.1116874E+01 -0.9965903E+00 -0.1175041E+01 -0.9287388E+00   w
    %4 -0.3808376E-01  0.2716607E+00 -0.3105235E+00  0.2321461E+00 -0.6033103E+00  0.4782076E+00   w_a    
\Omega_m = 0.301 \pm 0.008, w_0 = -1.042 \pm 0.067, w_a = -0.07 \pm 0.29.
%    1  0.3014353E+00  0.7759923E-02  0.2974325E+00  0.3048882E+00  0.2889838E+00  0.3152269E+00   \Omega_m
%    2  0.6887652E+00  0.8760036E-02  0.6797134E+00  0.6978279E+00  0.6703971E+00  0.7044224E+00   h
%    3 -0.1041626E+01  0.6732817E-01 -0.1107730E+01 -0.9768319E+00 -0.1172149E+01 -0.8979017E+00   w
%    4 -0.7173374E-01  0.2860547E+00 -0.3572176E+00  0.2107347E+00 -0.6775045E+00  0.4558817E+00   w_a    
\end{equation}
%$$.
While the central values of parameters do not shift appreciably,
the error bars of $w_0$ and $w_a$ are reduced by 38.4\% and 29.7\%, respectively.% $$-40\%$ by adding our method into the analysis.

@@

\bibitem{Li2016}%[Li et al.(2016)]
Li, X.-D., Park, C., \& Sabiu, C.G., et al. 2016, ApJ, 832, 103

\bibitem{2012IJMPD..2130002Y}%[Yoo \& Watanabe(2012)]
Yoo, J., \& Watanabe, Y.\ 2012, International Journal of Modern Physics D, 21, 1230002

\bibitem{AP1979}%[Alcock \& Paczynski(1979)]
Alcock, C., \& Paczynski, B. 1979, Nature, 281, 358

\bibitem{Outram2004}%[Outram et al.(2004)]
Outram, P.J., Shanks, T., Boyle, B.J., Croom, S.M., Hoyle, F., Loaring, N.S., 
Miller, L., \& Smith, R.J. 2004, MNRAS, 348, 745

\bibitem{Blake2011}%[Blake et al.(2011)]
Blake, C., Glazebrook, K., \& Davis, T. M., 2011, MNRAS, 418, 1725

\bibitem{Alam2016}%[Alam et al.(2016)]
Alam, S., Ata, M., \& Bailey, S., et al. 2016,
submitted to MNRAS (arXiv:1607.03155)

\bibitem{Ballinger1996}%[Ballinger, Peacock \& Heavens 1996]
Ballinger, W.E., Peacock, J.A., \& Heavens, A.F. 1996, MNRAS, 282, 877

\bibitem{Marinoni2010}%[Marinoni \& Buzzi(2010)]
Marinoni, C., \& Buzzi, A. 2010, Nature, 468, 539

\bibitem{Jennings2011}%[Jennings et al.(2011)]
Jennings, E., Baugh, C.M., \& Pascoli, S. 2011, MNRAS, 420, 1079

\bibitem{Ryden1995}%[Ryden(1995)]
Ryden, B.S. 1995, ApJ, 452, 25

\bibitem{LavausWandelt1995}%[Lavaux \& Wandelt(2012)]
Lavaux, G., \& Wandelt, B.D. 2012, ApJ, 754, 109

\bibitem{Qingqing2016}%[Mao et al. (2016)]
Mao, Q., Berlind, A.A., Scherrer, R.J., et al. 2016, submitted to ApJ

\bibitem{Li2014}%[Li et al.(2014)]
Li, X.-D., Park, C., Forero-Romero, J., \& Kim, J. 2014, ApJ, 796, 137

\bibitem{Li2015}%[Li et al.(2015)]
Li, X.-D., Park, C., Sabiu, C.G., \& Kim, J. 2015, MNRAS, 450, 807

\bibitem{LB2002}%[Lewis \& Bridle (2002)]
Lewis, A., \& Bridle, S. 2002, Phys. Rev. D, 66, 103511

\bibitem{Planck2015}%[Ade et al. (2015)]
Ade, P.A.R., Aghanim, N., \& Arnaud, M., et al. 2016, A\&A, 594, A13

\bibitem{Anderson2013}%[Anderson et al.(2013)]
Anderson, L., Aubourg, \'E., \& Bailey, S. et al. 2014, MNRAS, 441, 24

\bibitem{6dFGS}%[Beutler et al.(2011)]
Beutler, F., Blake, C., \& Colless, M., et al. 2011, MNRAS, 416, 3017

\bibitem{MGS}%[Ross et al.(2015)]
Ross, A.J., Samushia, L., \& Howlett, C., et al. 2015, MNRAS, 449, 835

\bibitem{JLA}%[Betoule et al.(2014)]
Betoule, M., Kessler, R., \& Guy, J., et al. 2014, A\&A, 568, 32

\bibitem{Riess2011}%[Riess et al.(2011)]
Riess, A.G., Macri, L., \& Casertano, S., et al. 2011, ApJ, 730, 119

\bibitem{E14H0}%[Efstathiou (2014)]
Efstathiou, G. 2014, MNRAS, 440, 1138

\bibitem{HR4}%[Kim et al.(2015)]
Kim, J., Park, C., L'Huillier, B., \& Hong, S. E. 2015, JKAS, 48, 213

%\bibitem{Lee12}
%\bibinfo{author}{Lee}, E.~J., {Murray}, N., {Rahman}, M. 
%\newblock \bibinfo{title}{Milky Way Star-forming Complexes and the Turbulent Motion of the Galaxy's Molecular Gas.}
%\newblock{\it Astrophys. \ J.}{\bf\, 752}, 146-159 (2012).

%%%% For methods
\bibitem{Reidetal:2016}%[Reid et al.(2016)]
Reid, B., Ho, S., \& Padmanabhan, N., et al.  2016, MNRAS, 455, 1553

\bibitem{komatsu 2011}%[Komatsu et al.(2011)]
Komatsu, E., Smith, K. M., \& Dunkley, J., et al. 2011, ApJS, 192, 18

\bibitem{hong2016}%[Hong et al.(2016)]
Hong, S.E., Park, C.,\&  Kim, J. 2016, ApJ, 823, 103

\bibitem{MDPATCHY}%[Kitaura et al.(2015)]
Kitaura, F.S., Rodriguez-Torres, S., Chuang, C.-H., et al.2016, MNRAS, 456, 4156

\bibitem{Hartlap}%[Hartlap et al.(2006)]
Hartlap J., Simon P. \& Schneider P. [astro-ph/0608064].

\bibitem{Percival2014}%[Percival et al.(2014)]
Percival, W.J., Ross, A.J., \& S\'{a}nchez, A.G., et al. 2014, MNRAS, 439, 2531

@@
